Haul-out behavior and aerial survey detectability of seals in the Bering and Chukchi seas

### 2022-04-07 analysis/paper/London_HauloutBeahvior.Rmd
minor improvements to Data Availability

This manuscript was developed as a reproducible research compendium. Data and
code are available on GitHub (https://github.com/jmlondon/berchukHaulout) and
major versions archived at Zenodo (https://doi.org/10.5281/zenodo.4638221).
Original data sources for telemetry are archived at the United States Animal
Telemetry Network.

>>>>

This manuscript was developed as a reproducible research compendium. All data and
code are available on GitHub (https://github.com/jmlondon/berchukHaulout) and
major versions archived at Zenodo (https://doi.org/10.5281/zenodo.4638221).
Original data sources for telemetry are archived
at the United States Animal Telemetry Network, archived at Movebank, or
associated with other published manuscripts (see supplemental material S1).
